Sweat electrolytes and CFTR activity in the era of CFTR modulators

### 2024-09-13 Edith Zemanick/Sweat Test/sweat_test_analysis.qmd
Update sweat_test_analysis.qmd

@@

```{r}
df %>%
  filter(!is.na(TotalGenotypeFunction)) %>%
  select(
    Diagnosis, Genotypes1, Genotypes2, Genotype1Function, Genotype2Function,
    TotalGenotypeFunction, Na, K, Cl
  ) %>%
  droplevels(.) %>%
  tbl_summary(by = Diagnosis)
```

```{r}
df %>%
  filter(!is.na(TotalGenotypeFunction)) %>%
  ggplot(
    aes(x = Cl, y = TotalGenotypeFunction, color = Diagnosis, group = Diagnosis)
  ) +
  geom_point() +
  geom_smooth(method = "lm", se = F) +
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank())

>>>>

#| message: false

@@

```{r}
#| message: false
df %>%
  filter(!is.na(TotalGenotypeFunction)) %>%
  select(
    Diagnosis, Genotypes1, Genotypes2, Genotype1Function, Genotype2Function,
    TotalGenotypeFunction, Na, K, Cl
  ) %>%
  droplevels(.) %>%
  tbl_summary(by = Diagnosis)
```

```{r}
#| message: false
#| warning: false
df %>%
  filter(!is.na(TotalGenotypeFunction)) %>%
  ggplot(
    aes(x = Cl, y = TotalGenotypeFunction, color = Diagnosis, group = Diagnosis)
  ) +
  geom_point() +
  geom_smooth(method = "lm", se = F) +
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank())
